GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers

### 2015-03-30 doc/report/survey/article.tex
changes to survey to make tables and also list

@@

\subsection{Electricity pricing} 
We use the day-ahead hourly electricity prices to get the electricity cost of the data center which will enable us to provision workloads efficiently. Moreover, the prices in the day-ahead market fluctuate smoothly and can be predicted using time series forecasting techniques.
\subsection{Energy source in data centers}
To meet the energy requirements of data centers there is increasing adoption of renewable energy supply techniques (solar, wind). This has resulted in data centers being powered at least partially with green energy. We wish to effectively use the green energy to reduce costs. 
\subsection{Cooling techniques employed}
The other second generation solution of energy efficient data center is the use of air economizers in data centers.An air-side economizer brings outside air into a building and distributes it to the servers. This can lead to a significant savings in cooling energy of the data center.

We will study each of these factor individually and look at their impact on the cost. Based on this, we will devise an appropriate optimization technique which will minimize the energy cost while obeying all the constraints.

@@

 \subsection{Study real-time and synthetic workloads} We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011. This process is challenging because task-IDs, job-IDs are obfuscated for security reasons. Resources utilization such as CPU and memory has been normalized with the maximum resource usage. We are also studying synthetic workloads that are generated by sampling historical MapReduce cluster traces. Tentatively we would complete this by 10\textsuperscript{th}March,2015.
 \subsection{Data Center profile}In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-replicated data centers.We would complete this by 20\textsuperscript{th}March,2015.
\subsection{Feature Extraction} This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost. We aim to complete this by 5\textsuperscript{th}April,2015.
 \subsection{Implementing Optimization technique} This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs.We aim to complete this by 25\textsuperscript{th}April,2015.
\subsection{Evaluation} This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above.We aim to complete this by 7\textsuperscript{th}May,2015.

>>>>

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

@@

\begin{list2}
\item \textbf{Electricity pricing} We use the day-ahead hourly electricity prices to get the electricity cost of the data center which will enable us to provision workloads efficiently.\
\item \textbf{Energy source in data centers} To meet the energy requirements of data centers there is increasing adoption of renewable energy supply techniques (solar, wind). This has resulted in data centers being powered at least partially with green energy. \
\item \textbf{Cooling techniques employed} The other second generation solution of energy efficient data center is the use of air economizers in data centers. An air-side economizer brings outside air into a building and distributes it to the servers. \
\end{list2}

@@

    \begin{tabular}{ | p{3cm} |l  |p{12cm}|  }
    \hline
    \bf{Item} & \bf{Deadline} & \bf{Description}   \\ \hline
    Study real-world and synthetic workloads & 10\textsuperscript{th} March,2015  & We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011.  \\ \hline
    Data Center profile & 20\textsuperscript{th} March,2015  & In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-distributed data centers. \\ \hline
    Feature Extraction & 25\textsuperscript{th} April,2015  & This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost \\ \hline
    Implementing Optimization technique & 5\textsuperscript{th} April,2015  & This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs \\ \hline
    Evaluation & 7\textsuperscript{th} May,2015  & This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above \\ \hline

    \end{tabular}
